Cooperative Kernels: GPU Multitasking for Blocking Algorithms

### 2017-02-17 write-ups/FSE/paper.tex
Typo only: remove trailing whitespaces
Simplify description of work-stealing exemple

\myfiglong\ref{fig:workstealing} shows a simplified version of a work
stealing kernel. Each thread receives a pointer to the
task queues, in global memory, initialized by the
host to contain the initial tasks. Each thread identifies
its workgroup via $\getgroupid$
(line~\ref{line:wksteal:getgroupid}), which is used as a queue id to access the relevant task queue. The
$\mathsf{pop\_or\_steal}$ function (line~\ref{line:wksteal:poporsteal})
is called by all threads of a workgroup.  Inside
$\mathsf{pop\_or\_steal}$ only the thread with a local id equal to $0$,
the \emph{master thread}, tries to pop a
task from the workgroup's queue, or to steal a task from a different
queue. The master thread uses local memory inside
$\mathsf{pop\_or\_steal}$ to ensure that the returned value is valid for
all threads of its workgroup. If a task was obtained, then all the
workgroup threads participate in the task processing (line~\ref{line:wksteal:processtask}).
This may lead to the creation of further tasks, which
the master thread pushes to the workgroup's queue.

>>>>

\myfiglong\ref{fig:workstealing} shows a simplified version of a work
stealing kernel. Each thread receives a pointer to the
task queues, in global memory, initialized by the
host to contain the initial tasks. Each thread identifies
its workgroup via $\getgroupid$
(line~\ref{line:wksteal:getgroupid}), which is used as a queue id to access the relevant task queue. The
$\mathsf{pop\_or\_steal}$ function (line~\ref{line:wksteal:poporsteal})
pops a task from the workgroup's queue or, if the queue is empty,
tries to steal a task from other queues.

% is called by all threads of a workgroup.  Inside
% $\mathsf{pop\_or\_steal}$ only the thread with a local id equal to $0$,
% the \emph{master thread}, tries to pop a
% task from the workgroup's queue, or to steal a task from a different
% queue. The master thread uses local memory inside
% $\mathsf{pop\_or\_steal}$ to ensure that the returned value is valid for
% all threads of its workgroup.

If a task was obtained, then the workgroup processes it
(line~\ref{line:wksteal:processtask}): during this operation, new tasks
may be created and pushed into the workgroup's queue.
